Open archaeology, open source?

### 2024-02-02 analysis/openarchaeo_collaboration.qmd
Remove unused package

library("english")
library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```

>>>>

library("english")
library("fs")
library("ggiraph")
library("ggraph")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```
